### 2015-02-06 cav-2015-tex/summary-heap.tex
Fixed a bug left over from a previous merge.

%\sjp{Up to now, no discussion of lazy initialization - what it is or
%  how it is being used.}  \nsr{A key insight to the summary heap is
%  that although many auxiliary or stack literals are created during
%  symbolic execution with lazy initialization, only input heap
%  references appear in the constraints expressing potential aliasing
%  relationships.}
A solver is used to reason over the aliasing relationships, and a
satisfying assignment uniquely identifies the set of aliasing
relationships that are representative of a concrete heap and its
shape. For example, if the solver assigns input heap variables
$\cfgnt{r}$ and $\cfgnt{r}^\prime$ such that $\cfgnt{r} =
\cfgnt{r}^\prime$ is true, then there exists some location $\cfgnt{l}$
and constraints $\phi$ and $\phi^\prime$ such that (i)
$\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; (ii)
>>>>>>> 49c83f34a0b5afd58adc4b6649b15e2cbc93437c
$\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
(iii) $\phi$ and $\phi^\prime$ hold in the aliasing assignments from
the solver.  In this way, the graph groups heaps with the conditions
under which those heaps exist so look-ups are non-recursive and
updates do not modify the path condition or require rewrites on
constraints.

>>>>

%\sjp{Up to now, no discussion of lazy initialization - what it is or
%  how it is being used.}  \nsr{A key insight to the summary heap is
%  that although many auxiliary or stack literals are created during
%  symbolic execution with lazy initialization, only input heap
%  references appear in the constraints expressing potential aliasing
%  relationships.}
A solver is used to reason over the aliasing relationships, and a
satisfying assignment uniquely identifies the set of aliasing
relationships that are representative of a concrete heap and its
shape. For example, if the solver assigns input heap variables
$\cfgnt{r}$ and $\cfgnt{r}^\prime$ such that $\cfgnt{r} =
\cfgnt{r}^\prime$ is true, then there exists some location $\cfgnt{l}$
and constraints $\phi$ and $\phi^\prime$ such that (i)
$\lp\phi\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r})$; (ii)
$\lp\phi^\prime\ \cfgnt{l}\rp \in \cfgnt{L}(\cfgnt{r}^\prime)$; and
(iii) $\phi$ and $\phi^\prime$ hold in the aliasing assignments from
the solver.  In this way, the graph groups heaps with the conditions
under which those heaps exist so look-ups are non-recursive and
updates do not modify the path condition or require rewrites on
constraints.
